Verifying Demonstrations

### 2020-04-21 paper/protocol-trusted.tex
Rewrites the trusted-witness protocol up to verification section

A prerequisite for this protocol is a one-to-one mapping between a persons real 
identity and a certificate (\ie a cryptographic key).
\Cref{ProtocolSetup} covers how Alice can obtain such a certificate.
It is a lighter version than in \cite{SelfCertifiedSybilFreePseudonyms} and not 
the full protocol of \cite{HowToWinTheCloneWars}.

@@

Before Alice can have her participation in any event counted by
\CROCUS, she needs to get an anonymous credential and corresponding
keys. This only needs to be repeated when the credential expires or is
lost, in analogy to a passport in terms of expected intervals. The
keys can be reused for an arbitrary number of protests or, given
careful choices in the PRF used for deriving identifiers, other
services that work with anonymous credentials.

We use the setup and registration phases of Anon-Pass~\cite{AnonPass} for
getting anonymous credentials, adapting only the notation to fit ours. 
%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key~\((k, 
  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
  it} to the \ac{CA} (or to any part thereof in a multi-party scenario).
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{fig:ProtocolOverview}.
The goal of \CROCUS is to generate and collect privacy-preserving
participation proofs that can be counted and verified. These proofs
consist of proof shares that are constructed as depicted in
\cref{fig:ProofFig}. The protocol phases are given in
\cref{fig:ProtocolOverview} and described below.

@@

\emph{Creation of a protest: the manifesto.}
The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text, in
practice at minimum a name.
The organizer then distributes this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree with the cause, they will use the knowledge of the
manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest uses the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.
The protester also fetches a time-correlated random value, \(t_s\), from 
\(\TS\), \(t_s\gets \TSget\).

\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
The witness simply gets a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
set the start of the time interval of creation for the proof share.

\emph{Participation: \(\pi\gets
    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and 
the witness construct the proof share of the protester (\cref{fig:ProofFig}).

The protester sends \(\pid\) and \(t_s\) to the witness.
Then they run the protocol \[
  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
\] (see \cref{ACacAlg}), \(k\) and \(r\) are part of \(\sk_P\).
Note that the \acf{PK} in \cref{ACacAlg} must be
run as a \iacf{PPK}, which we do by distance bounding.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The protester commits the proof-share data to the ledger~\(L\) and receives the 
proof of commitment, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
The sooner this is done, the higher the precision for the time-dependent 
eligibility criterion will be for later counting.
The remaining operations are not time critical.

The protester computes \iac{NIZK} proof \(\corr_{\pid}\), which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \corr_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the protester uploads the tuple \[
  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \corr_{\pid})
\] for permanent storage, \(\TSsubmit[\psh_P]\).

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness, like the protester, commits the proof-share data to the 
ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
%(This is to make the time interval as early as possible, whoever is the faster 
%will submit it.) \sonja{but both do}
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage on the ledger, \(\TSsubmit[\psh_W]\).

\begin{figure*}
  \centering
  \small
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
    \end{align*}
    \caption{Join and participation.}
  \end{subfigure}
  \hfill
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      P\colon & t_e\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\wid})],\quad \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\pid})],\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
    \caption{Submission.}
  \end{subfigure}
  \caption{%
    An overview of \CROCUS participation.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
   public ledger for permanent storage \(S\). Note that \pid  always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure*}
%\normalsize

>>>>

A prerequisite for this protocol is a one-to-one mapping between a persons real 
identity and a certificate (\ie a cryptographic key).
\Cref{ProtocolSetup} covers how Alice can obtain such a certificate.
It is a lighter version than in~\cite{SelfCertifiedSybilFreePseudonyms} and not 
the full protocol of~\cite{HowToWinTheCloneWars}.

@@

Before Alice can have her participation in any event counted, she must get a 
certificate that ensures Sybil-freeness.
This is only done once\footnote{%
  It is repeated when the credential expires, in analogy to a passport in terms 
  of expected intervals.
}.
The keys can be reused for an arbitrary number of protests or, given
careful choices in the \ac{PRF} used for deriving identifiers, other
services that work with anonymous credentials.

We use the setup and registration phases of 
Anon-Pass~\cite{AnonPass}\footnote{%
  This version is slightly adapted (improves efficiency) from the original 
  version by \textcite{HowToWinTheCloneWars}.
} for getting the certificate, adapting only the notation to fit ours. 
%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.

\paragraph*{Setup: \((\spk, \ssk)\gets \CROCUSsetup\)}

During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\paragraph*{Registration: \(\sk\gets 
\Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\)}

During the registration phase, each participant
generates a secret key~\((k, r)\) and
obtains a signature on it by the \ac{CA} \emph{but without revealing it} to the 
\ac{CA} (or to any part thereof in a decentralized \ac{CA} scenario).
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{protocol-overview-trusted}.
The goal of our protocol is to generate and collect privacy-preserving
participation proofs that can be counted and verified. These proofs
consist of proof shares that are constructed as depicted in
\cref{fig:ProofFig}.
They are constructed through an interactive protocol between the protester and 
the witness, as depicted in \cref{protocol-overview-trusted} and described below.

@@

\paragraph*{Creation of a protest: the manifesto}

The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text, in
practice at minimum a name.
The organizer then distributes this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree with the cause, they will use the knowledge of the
manifesto to join the protest.

\paragraph*{Joining as a protester:
  \((\pid)\gets \CROCUSjoin[_P][\mfst]\)}

In the terminology of \textcite{SelfCertifiedSybilFreePseudonyms}, the 
manifesto~\(\mfst\) is the context and it yields an identity domain.
A protester who wants to join the protest uses the manifesto~\(\mfst\) to
compute an identifier for the cause (the context) by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\)\footnote{%
  The result should be compared to that received from the organizer to check 
  that the \(\cid\) indeed is correct.
  This is to avoid that protesters use different \(\cid\)s for semantically 
  equivalent manifestos~\(\mfst\).
  However, we omit this in the protocol for readability.
}.
Afterwards, this is used to create the protester's protest-specific 
pseudonym~\(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.

\paragraph*{Joining as a witness}

The witness does not have to do anything to join as a witness.
That the witness is trusted by the verifier means that the verifier trusts that 
the witness can
\begin{enumerate*}
  \item determine the time of an interaction with a protester,
  \item determine the its own location during that interaction
    and
  \item will run the protocol as an honest witness with the potentially 
    malicious protester.
\end{enumerate*}

\paragraph*{Participation:
  \(\pi\gets
    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\)}

In the participation phase, the protester and 
the witness construct the proof share of the protester (\cref{fig:ProofFig}).

The protester sends \(\pid\) to the witness.
Then they run the protocol \[
  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
\] (see \cref{ACacAlg}), \(k\) and \(r\) are part of \(\sk_P\).
Note that the \acf{PK} in \cref{ACacAlg} must be
\iacf{PPK} (\ie a \acl{PK} with distance bounding).
We use the protocol of \textcite{DB-Schnorr}, which does exactly this.
If the protocol succeeds, the witness will compute \(\wid \gets 
\ACprf[_{\sk_W}][\pid]\) and send \((\wid, t, l)\) to the protester, where 
\(t\) is the current time and \(l\) is the witness' current location.

\paragraph*{Submission:
  \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t, l]\)}

In the submission phase, the proof shares are be made available for the 
verifier.
\Ie the verifier must be able to verify that a proof was actually issued by a 
witness.

To achieve this, the witness computes \iac{NIZK} proof~\(\corr_{\wid}\), 
proving the correctness of \(\wid\) while also signing the time~\(t\) and 
location~\(l\).
More specifically, we have that
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\sskw}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t, l).
\end{multline*}
Finally, the complete proof share is the tuple \[
  \psh_W = (\cid, \pid, \wid, t, l, \corr_{\wid}).
\]

For individual and universal verifiability, the proof should be published on 
some permanent storage, such as the ledger~\(\TS\) by running 
\(\TSsubmit[\psh_W]\) (\cref{ledger}).

Note that it does not matter if it is the witness or the protester who makes 
\(\psh_W\) available to the verifier.
The witness could compute \(\psh_W\) during the protest and give to the 
protester immediately, but we separate these steps to show that the witness can 
postpone those extra computations while potentially running on battery.

Now, the witness is anonymous here.
For the verifier to recognize a proof on some publicly available storage as 
issued by a trusted witness there could be another \ac{CA}, say \(\CA'\), which 
issues credentials to witnesses.
\(\CA'\) could be run by a news paper, trusted to only issue credentials to 
trustworthy witnesses.

Another solution would be that the witness simply signs the tuple \((\cid, 
\pid, t, l)\) with a key that is tied to the witness' identity.
However, that would allow tracking and thus the anonymity set of the protester 
would shrink.

Note also that the prover need not compute any \ac{NIZK} proof of the 
correctness of \(\pid\) since the witness is trusted to have verified this (as 
part of the distance bounding).

\begin{figure*}
  \centering
  \small
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid]
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      %W\to P\colon & (\wid, t, l)
    \end{align*}
    \caption{Join and participation}
  \end{subfigure}
  \hfill
  \begin{subfigure}{\columnwidth}
    \begin{align*}
      W\colon & \TSsubmit[(\cid, \pid, \wid, t, l, \corr_{\wid})],\quad 
      \text{where} \\
        & \corr_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' =
              \ACblind[\ACsign[_{\sskw}][\sk_W]]\mright\} \\
        & \qquad\qquad (\cid, \pid, \wid, t, l)
    \end{align*}
    \caption{Submission}
  \end{subfigure}
  \caption{%
    An overview of the protocol with trusted witnesses.
    The organizer~\(O\) broadcasts the manifesto.
    The protester~\(P\) with pseudonym~\(\pid\) in the context of the protest 
    (\(\cid\)),
    the witness~\(W\) with pseudonym~\(\wid\) in the context of that protester 
    and
    their computations are as in \cref{fig:ProofFig}.
    Finally, \(W\) submits the proof share to a public ledger~\(\TS\) for 
    permanent storage.
  }%
  \label{protocol-overview-trusted}
\end{figure*}
%\normalsize
